Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-03-19 curriculo/cv.tex
[]

  \entry
    {01 2016\\(ongoing)}
    {Applications Development}
    {Bullray-CIT\\1000€/month (part time)}
    {\emph{Development of a user interface for a bank's security device that is synchronized with servers. Microcontroller sensors information receival through \underline{USB} (\underline{org.usb4java}), user interface with \underline{JavaFX} and network camera discovery through nmap (using \underline{org.nmap4j}) } }

 \entry
    {11 2015\\(2 months)}
    {Android Development}
    {Bullray-CIT\\1000€/month (part time)}
    {\emph{Optimization and bug resolution of an \underline{Android} application that uploads GPS, camera and microphone data in background.}}

\entry
    {08 2015\\(standby)}
    {Systems Development}
    {Bullray-CIT\\1000€/month (part time)}
    {\emph{Development and configuration of a streaming server that supports receiving and recording video from authenticated users through \underline{ffmpeg}. I tried \underline{FFServer}, \underline{nginx with rtmp module} and \underline{Wowza Streaming Server}, the final decision was \underline{Kurento Media Server} with an \underline{RTP} endpoint for receiving video from network cameras and a \underline{WebRTC} endpoint for delivering the video to web browsers. }}

@@

  \entry
    {02 2015\\(ongoing)}
    {Full-Stack Web Development}
    {Bullray-CIT\\1000€/month (part time)}
    {\emph{Development of a solution for a generic incident handling server, support for real time monitoring through \underline{WebSockets}. Experience with \underline{PlayFramework}, \underline{MongoDB} (with the official Java Driver), \underline{Maven}, \underline{jQuery} and \underline{Bootstrap}.}}

  \entry
    {11 2014\\(4 months)}
    {Full-Stack Web Development}
    {Bullray-CIT\\1000€/month (part time)}
    {\emph{Development of an architecture for a chat application. Experience with \underline{Android}, \underline{PlayFramework}, \underline{MongoDB} (with Morphia), \underline{jQuery} and \underline{Bootstrap}. Message synchronization through HTTP long polling.}}
  \entry
    {04 2014\\(6 months)}
    {Scientific Initiation Scholarship}
    {INESC\\385€/month (part time)}
    {\emph{Frontend Development for Provide Results's Bimk project. Experience with \underline{PlayFramework}, \underline{Revit API} and \underline{GIT}.}}
  \entry
    {09 2013\\(6 months)}
    {Scientific Initiation Scholarship}
    {CEG-IST\\385€/month (part time)}
    {\emph{Programming a Decision Analysis Software (MACBETH) with \underline{WPF}. Development of an algorithm to suggest judgements based on past decisions using \underline{lpsolve}.}}
  \entry
    {08 2013\\(2 weeks)}
    {Summer Work}
    {LCG}
    {\emph{Frontend development for a Decision Analysis Software using \underline{ASP.NET}. }}
  \entry
    {11 2012}
    {Pizza Night Competition}
    {Microsoft Lisbon Experience}
    {\emph{2º place on Windows Phone Category} with \emph{Infinity Edge} game.}
  \entry
    {08 2006\\(1 month)}
    {Garbage Collector}
    {Jovens em Movimento, Oeiras\\120€/month(full time)}
    {Cleaning and maintenance of public spaces.}

@@

\begin{entrylist}
  \entry
    {2015}
    {Bomb Raider}
    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{Google Play}}
    {Bomb Raider is a simple singleplayer and multiplayer game where the goal is destroying all enemies in the map. I used \underline{OpenGLES} and \underline{WiFi-Direct} to develop this \underline{Android} game.}

>>>>

  \entry
    {01 2016\\(ongoing)}
    {Applications Development}
    {Bullray-CIT}
    {\emph{Development of a user interface for a bank's security device that is synchronized with servers. Microcontroller sensors information receival through \underline{USB} (\underline{org.usb4java}), user interface with \underline{JavaFX} and network camera discovery through nmap (using \underline{org.nmap4j}) } }

 \entry
    {11 2015\\(2 months)}
    {Android Development}
    {Bullray-CIT}
    {\emph{Optimization and bug resolution of an \underline{Android} application that uploads GPS, camera and microphone data in background.}}

\entry
    {08 2015\\(standby)}
    {Systems Development}
    {Bullray-CIT}
    {\emph{Development and configuration of a streaming server that supports receiving and recording video from authenticated users through \underline{ffmpeg}. I tried \underline{FFServer}, \underline{nginx with rtmp module} and \underline{Wowza Streaming Server}, the final decision was \underline{Kurento Media Server} with an \underline{RTP} endpoint for receiving video from network cameras and a \underline{WebRTC} endpoint for delivering the video to web browsers. }}

@@

  \entry
    {02 2015\\(ongoing)}
    {Full-Stack Web Development}
    {Bullray-CIT}
    {\emph{Development of a solution for a generic incident handling server, support for real time monitoring through \underline{WebSockets}. Experience with \underline{PlayFramework}, \underline{MongoDB} (with the official Java Driver), \underline{Maven}, \underline{jQuery} and \underline{Bootstrap}.}}

  \entry
    {11 2014\\(4 months)}
    {Full-Stack Web Development}
    {Bullray-CIT}
    {\emph{Development of an architecture for a chat application. Experience with \underline{Android}, \underline{PlayFramework}, \underline{MongoDB} (with Morphia), \underline{jQuery} and \underline{Bootstrap}. Message synchronization through HTTP long polling.}}
  \entry
    {04 2014\\(6 months)}
    {Scientific Initiation Scholarship}
    {INESC}
    {\emph{Frontend Development for Provide Results's Bimk project. Experience with \underline{PlayFramework}, \underline{Revit API} and \underline{GIT}.}}
  \entry
    {09 2013\\(6 months)}
    {Scientific Initiation Scholarship}
    {CEG-IST}
    {\emph{Programming a Decision Analysis Software (MACBETH) with \underline{WPF}. Development of an algorithm to suggest judgements based on past decisions using \underline{lpsolve}.}}
  \entry
    {08 2013\\(2 weeks)}
    {Summer Work}
    {LCG}
    {\emph{Frontend development for a Decision Analysis Software using \underline{ASP.NET}. }}
  \entry
    {11 2012}
    {Pizza Night Competition}
    {Microsoft Lisbon Experience}
    {\emph{2º place on Windows Phone Category} with \emph{Infinity Edge} game.}
  \entry
    {08 2006\\(1 month)}
    {Garbage Collector}
    {Jovens em Movimento, Oeiras}
    {Cleaning and maintenance of public spaces.}

@@

\begin{entrylist}
%  \entry
%    {201?}
%    {My personal website}
%    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{henrique.rocha.pt}}
%    {I like PlayFramework, but I still like more to learn different technologies, that's why I did this website using ???, just for fun.}

  \entry
    {2015}
    {Bomb Raider}
    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{Google Play}}
    {Bomb Raider is a simple singleplayer and multiplayer game where the goal is destroying all enemies in the map. I used \underline{OpenGLES} and \underline{WiFi-Direct} to develop this \underline{Android} game.}
